Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-21 paper/structureScene.tex
move table 1
done with revision

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{RbQ} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}. %\ja{And BOF?}

The clustering for the \emph{RbQ} methods is done using $k$-means$++$ \cite{arthur2007k}, an augmented version of $k$-means with a more robust initialization procedure. Three numbers of clusters are tested: $8$, $16$ and $32$.

@@

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset.\label{table:dcase2016}}
\begin{tabular}{lccc}
Features & MFCCs & log-scattering & log-scattering \\
Subset & development & development & evaluation \\
\midrule
beach & $58.3 \pm 28.2$ & $83.5 \pm \phantom{0}7.1$ & $80.8$\\
bus & $58.2 \pm 25.4$ & $88.8 \pm 11.4$ & $92.3$ \\
cafe/restaurant & $77.4 \pm 14.7$ & $64.5 \pm \phantom{0}8.3$ & $50.0$ \\
car & $92.3 \pm \phantom{0}7.7$ & $94.9 \pm \phantom{0}6.1$ & $96.2$ \\
city\_center & $96.4 \pm \phantom{0}3.8$ & $91.7 \pm \phantom{0}9.4$ & $84.6$ \\
forest\_path & $67.7 \pm 30.8$ & $93.8 \pm \phantom{0}7.8$ & $96.2$ \\
grocery\_store & $44.7 \pm 24.8$ & $90.9 \pm \phantom{0}6.9$ & $84.6$ \\
home & $44.8 \pm 15.3$ & $56.2 \pm 23.9$ & $80.8$ \\
library & $54.6 \pm 20.3$ & $82.0 \pm 13.0$ & $65.4$ \\
metro\_station & $94.7 \pm \phantom{0}6.8$ & $96.0 \pm \phantom{0}2.3$ & $96.2$ \\
office & $95.7 \pm \phantom{0}7.5$ & $87.5 \pm 21.7$ & $100$ \\
park & $52.4 \pm 10.4$ & $75.4 \pm \phantom{0}7.4$ & $65.4$ \\
residential\_area & $53.2 \pm 17.0$ & $44.2 \pm 15.0$ & $69.2$ \\
train & $44.5 \pm 23.1$ & $58.3 \pm 10.0$ & $53.8$ \\
tram & $52.1 \pm 11.9$ & $83.7 \pm 12.2$ & $96.2$ \\
\bottomrule
Average & $65.8 \pm \phantom{0}8.0$ & $79.4 \pm \phantom{0}3.0$ & $80.8$ \\
\end{tabular}
\end{center}

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (RbQ) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes than \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, all the \emph{RbQ} approaches perform equivalently. As such, one can conclude that the use of MFCCs allows us to retrieve closely related scenes, but their lack of discriminative capabilities making the cluster selection/weighting step useless for not so closely related scenes of the same class.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{bw/unsupervised_test2}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}

>>>>

The evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}. %\ja{And BOF?}

The scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) is set to 10 \% of the number of data points to cluster, being the number of scenes for \emph{early} and the number of cluster for RbQ approaches. 
The clustering for the \emph{RbQ} approaches is done using plain $k$-means with random initialization and 200 replications. For each method, the numbers of clusters is set to the value among $8$, $16$ and $32$ that leads to the best $p@9$ on the training set.

@@

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset.\label{table:dcase2016}}
\begin{tabular}{lccc}
Features & MFCCs & log-scattering & log-scattering \\
Subset & development & development & evaluation \\
\midrule
beach & $58.3 \pm 28.2$ & $83.5 \pm \phantom{0}7.1$ & $80.8$\\
bus & $58.2 \pm 25.4$ & $88.8 \pm 11.4$ & $92.3$ \\
cafe/restaurant & $77.4 \pm 14.7$ & $64.5 \pm \phantom{0}8.3$ & $50.0$ \\
car & $92.3 \pm \phantom{0}7.7$ & $94.9 \pm \phantom{0}6.1$ & $96.2$ \\
city\_center & $96.4 \pm \phantom{0}3.8$ & $91.7 \pm \phantom{0}9.4$ & $84.6$ \\
forest\_path & $67.7 \pm 30.8$ & $93.8 \pm \phantom{0}7.8$ & $96.2$ \\
grocery\_store & $44.7 \pm 24.8$ & $90.9 \pm \phantom{0}6.9$ & $84.6$ \\
home & $44.8 \pm 15.3$ & $56.2 \pm 23.9$ & $80.8$ \\
library & $54.6 \pm 20.3$ & $82.0 \pm 13.0$ & $65.4$ \\
metro\_station & $94.7 \pm \phantom{0}6.8$ & $96.0 \pm \phantom{0}2.3$ & $96.2$ \\
office & $95.7 \pm \phantom{0}7.5$ & $87.5 \pm 21.7$ & $100$ \\
park & $52.4 \pm 10.4$ & $75.4 \pm \phantom{0}7.4$ & $65.4$ \\
residential\_area & $53.2 \pm 17.0$ & $44.2 \pm 15.0$ & $69.2$ \\
train & $44.5 \pm 23.1$ & $58.3 \pm 10.0$ & $53.8$ \\
tram & $52.1 \pm 11.9$ & $83.7 \pm 12.2$ & $96.2$ \\
\bottomrule
Average & $65.8 \pm 19.3$ & $79.4 \pm 15.6$ & $80.8 \pm 16.4$ \\
\end{tabular}
\end{center}

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (RbQ) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. This result is in line with the findings of \cite{lagrange:hal-01082501}. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes than \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

Considering the $p@5$ as in \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} as our metric, the use of the log-scattering transform versus MFCCs increases the performance  from 0.31 to 0.49 and the use of the relevance based quantization approach using the closest similarity (RbQ-c) further improves the performance to 0.54 for a global increase of 0.23.

%The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, all the \emph{RbQ} approaches perform equivalently. As such, one can conclude that the use of MFCCs allows us to retrieve closely related scenes, but their lack of discriminative capabilities making the cluster selection/weighting step useless for not so closely related scenes of the same class.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{bw/unsupervised_test2}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}
